Digital History in Finland, 1488-1828

### 2016-06-21 inst/examples/manuscript-krakow.Rmd
Rmd update

Digital History in Finland, 1488-1828
==============

@@

@@

 * Library catalogues (Fennica & Kungliga)
 * Material also from the funding application
 * Open data analytical ecosystem
 * Github links
 * Explanation

>>>>

Printing in a Periphery: a Quantitative Study of Finnish Knowledge Production, 1640-1828
==============

@@

Aatehistoria ja digitaalisten  aineistojen mahdollisuudet ([Tolonen & Lahti (2015)](http://www.ennenjanyt.net/2015/08/aatehistoria-ja-digitaalisten-aineistojen-mahdollisuudet/))

We have prepared open data analytical ecosystem for in-depth analysis of such data collections ([Lahti, Ilomaki, Tolonen (2015)](http://doi.org/10.18352/lq.10112)).

@@

Library catalogues contain rich metadata on...

Here we analyse Fennica & Kungliga..

Further draft text in the funding application..?

We have prepared open data analytical ecosystem for in-depth analysis of such data collections ([Lahti, Ilomaki, Tolonen (2015)](http://doi.org/10.18352/lq.10112)).

In summary, the data analytical ecosystem does ..

Reading, parsing, cleaning up, enriching, summarizing, analysis, visualization, figures and tables..

Full source code to reproduce these analyses are available via Github ([Fennica](https://github.com/rOpenGov/fennica/); [Kungliga](https://github.com/rOpenGov/kungliga/)).
